---
title: "team"
author: "HanSun, XinyiZhu"
date: "2020.2.10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
choco <- read.csv("http://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
```
### What did you do in lab1 and how this time is different
We learned to push and pull the documents through the Git. In lab2 we also did the data exploration on chocolate rating.

### Question set(team)
#### 1. What is the overall number of chocolate rated?
```{r}
library(plyr)
count(choco$Rating)
str(choco)
```
#### 2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
rela <- table(choco$Review.Date, choco$Rating)
barplot(rela)
```
#### 3. Which are the three locations with the most ratings? How do ratings compare across these company locations?
```{r}
choco3.5<- choco[choco$Rating == 3.5, ]
choco3.5$Company.Location
loc<- choco3.5$Company.Location
names(loc)<-choco3.5$Company.Location
sort(loc)
sort(loc, decreasing = TRUE)
biggest3<-sort(loc, decreasing = TRUE)[1:3]
biggest3
```
#### 4. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

### In 2015, which company has the lowest rating?

#### 5.Answer the question from the dataset.
```{r}
## In 2015, which company has the lowest rating?
date2015<- choco[choco$Review.Date == 2015, ]
date2015$City
length(date2015$Company)#length: length of a vector
length(unique(date2015$Company))
date2015$Rating
date2015[which.min(date2015$Rating), ]
```
### Therefore, 1011 Love Bar has the lowest rating in 2015.

#### 6. Write one paragraph commenting on the workflow.
###  In this Lab work, we collaborate with our teammates to practice "push and pull files" through github in terminal and R fundamentals and basic graphics, such as finding a min value and a bar plot. And, we learnt how to create an interesting question by ourselves based on the dataset and solved it. 

