---
title: "team"
author: "HanSun, XinyiZhu"
date: "2020.2.10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
choco <- read.csv("http://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
```
### What did you do in lab1 and how this time is different
We learned to push and pull the documents through the Git. In lab2 we also did the data exploration on chocolate rating.

### Question set(team)
#### 1. What is the overall number of chocolate rated?
```{r}
library(plyr)
count(choco$Rating)
str(choco)
```
#### 2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}

```
#### 3. Which are the three locations with the most ratings? How do ratings compare across these company locations?
```{r}

```
#### 4. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

#### 5.Answer the question from the dataset.

#### 6. Write one paragraph commenting on the workflow.
